Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-05-12 article.tex
Described exploratory study

Would a pathogen have only peptides that do not bind to
any HLA, a pathogen would be undetected. In that case, a mutation
that causes a pathogen to become detected by a host's immune
system, may be selected against. Also, would a pathogen have only
one epitope, there would be selection for a mutation to lose it.
If there are many, say hundreds, of epitopes, the selection to lose or
gain an epitope is expected to have little effect. The relation
between the fitness of a pathogen and the number of epitopes is unknown.

This study assumes a gradual fitness landscape, in which it always
(slightly) beneficial for a pathogen to lose an epitope.
Because this assumption needs to be correct for the research
to be viable, we did an
exploratory experiment (see 'Fitness landscape', 
subsection \ref{subsec:fitness_landscape}).
We concluded that the assumption may be correct.

>>>>

Would a pathogen have only peptides that do not bind to
any HLA, a pathogen would be undetected. In that case, one
can imagine that a mutation
that causes a pathogen to become detected by a host's immune
system, may be selected against. Also, would a pathogen have only
one epitope, one can imagine there would be selection for a mutation to lose it.
If there are, however, already many epitopes present in the
proteome, the selection to lose or gain an epitope is expected 
to have less or no effect.

\paragraph{Test that selection is additive}

This study assumes a gradual fitness landscape, in which it always
(slightly) beneficial for a pathogen to lose an epitope.
Because this assumption needs to be correct for the research
to be viable, we did an
exploratory experiment (see 'Fitness landscape', 
subsection \ref{subsec:fitness_landscape}).
We concluded that the assumption may be correct 
\richel{Let's assume for now}.
